Scikit-learn: machine learning without learning the machinery

### 2014-05-18 article.tex
Better data description

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{dblfloatfix}
%\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{minted}
\usepackage[numbers,square]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}
\usepackage{magazine-style}

@@

\paragraph{Some history}
%
Scikit-learn started circa 2007 as code from David Cournapeau and
Matthieu Brucher's PhD work, but dwindled down till 2010, year at which the
Parietal team from INRIA adopted the project, hiring a full time
engineer. Basics API were defined and an efficient binding of LibSVM
\cite{chang2011libsvm} gave the project a compelling advantage. In
December 2011, the first international sprint was organized with generous
funding from Google. At this point, the project has grown vastly beyond
INRIA into a worldwide open source effort.

@@

Discuss what we can learn from the wages examples. Introduce concepts of
overfitting, model complexity

\begin{figure}
    %\hspace*{-.015\linewidth}%
    \includegraphics[width=1.05\linewidth]{wage_data}%

    \caption{Wage as a function of years of experience and education,
    data from \cite{berndt1991}}
\end{figure}

\begin{figure}
    %\hspace*{-.015\linewidth}%
    \includegraphics[width=1.05\linewidth]{wage_data_random_forest}%

    \caption{Wage prediction from years of experience and education,
    using random forests}
\end{figure}

\begin{figure}
    \hspace*{-.015\linewidth}%
    \includegraphics[width=1.05\linewidth]{wage_data_linear_svm}%

    \caption{Wage prediction from years of experience and education,
    using a linear SVM}
\end{figure}

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
%\usepackage{dblfloatfix}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{minted}
\usepackage[numbers,square]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}
\usepackage{magazine-style}

@@

\paragraph{Some history}
%
Scikit-learn started circa 2007 as code from David Cournapeau and
Matthieu Brucher's PhD work, but dwindled down till 2010, year at which the
Parietal team from INRIA adopted the project, hiring a full time
engineer. Basics API were defined and an efficient binding of LibSVM
\cite{chang2011libsvm} gave the project a compelling advantage. In
December 2011, the first international sprint was organized with generous
funding from Google. Today, the project has grown vastly beyond
INRIA into a worldwide open source effort.

@@

\begin{figure}[b]
    %\hspace*{-.015\linewidth}%
    \includegraphics[width=1.05\linewidth]{wage_data}%

    \caption{Wage as a function of years of work experience and
    education; data from \cite{berndt1991}\label{fig:data}.}
\end{figure}

% Introduce and describe the data
Machine learning is about extracting rules from data, most often with the
goal of making decision on new data. As a simple example, we show on
Fig.\,\ref{fig:data} data about wages in the US, from \cite{berndt1991}:
11 features, including wage, number of years of education and of work
experience, on 534 individuals --samples in machine-learning
jargon. This data
Code downloading the data to reproduce the figures can be found on
\url{https://github.com/scikit-learn/SigMobile-paper}.
%
This data showcases many of the typical difficulties machine learning.
The samples are very irregularly distributed, as most individuals
finished their education after high-school. As a result, they are gapping
holes in the 2D plot education versus work experience, in which any
statistical analysis is extrapolation. The data is very noisy: for a
given education and work experience wages vary widely. This variability
can probably be explained with missing factors, such as sector of
activity, but adding them to the analysis creates a more complex picture,
in 3D or more, rather than 2D, with even more gaps.

% Show an example of learning, first with random forest, and introduce
% overfit, then with svms, and discuss model complexity and use linear
% models to link to convention statistics. Conclude with the difference
% with 1D and 2D, and introduce the curse of dimensionality.
Discuss what we can learn from the wages examples. Introduce concepts of
overfitting, model complexity

\begin{figure}[b]
    %\hspace*{-.015\linewidth}%
    \includegraphics[width=1.05\linewidth]{wage_data_random_forest}%

    \caption{Wage prediction from years of work experience and education,
    using random forests.}
\end{figure}

\begin{figure}[b]
    \hspace*{-.015\linewidth}%
    \includegraphics[width=1.05\linewidth]{wage_data_linear_svm}%

    \caption{Wage prediction from years of work experience and education,
    using a linear SVM.}
\end{figure}
